An observational study of papers published in _PLOS ONE_ and studies posted to a trial registry.

### 2021-04-20 manuscript/asa_template/asa_template.Rmd
update tex file

![\label{fig:plot-10-topics}Topic clouds summarising common terms in _PLOS ONE_ statistical methods sections assuming ten clusters](figures/plosone.10topics.jpg)

>>>>

![\label{fig:plot-10-topics}Topic clouds summarising common terms in _PLOS ONE_ statistical methods sections assuming ten clusters](figures/figure2.jpg)
